\documentclass[12pt]{article}
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{amssymb}
\usepackage[T1]{fontenc}
\title{Dictating mathematics into Scientific notebook using Mathfly}
\author{Mike Roberts}
\begin{document}
\maketitle
\tableofcontents

\section{Introduction}
\begin{itemize}
\item All of these bindings can be easily changed by modifying modifying mathfly/config/scientific\_notebook.toml in any text editor or saying "configure Scientific Notebook" while the module is enabled.
\item (option a | option b) means that both commands will do the same thing.
\item Square brackets means that the word(s) inside are optional, the command will work with or without them.
\end{itemize}

\section{Basics}
\begin{tabularx}{\linewidth}{ l X}
new file & Create a new file \\
open file & Open a file \\
save file & Save a file \\
save as & Save as \\
print file & Print current document \\
export document & Export current document as .rtf \\
page preview & View a preview of the current document \\
toggle math & Inline mathematics \\
body math & Block mathematics \\
toggle text & Inline text \\
body text & Block text \\
evaluate & Evaluate expression \\
begin [bulleted] list & Begin a bulleted list \\
begin numbered list & Begin a numbered list \\
end list & End the current list \\
insert normal text & normal text \\
insert big text & \large{large text} \\
insert small text & \small{small text} \\
insert bold text & \textbf{bold text} \\
insert italic text & \textit{bold text} \\
insert bold symbols & $\mathbf{bold symbols}$ \\
insert centred text & Insert centred text \\
insert left text & Insert left justified text \\
insert right text & Insert right justified text \\
insert quotation & Insert a quotation \\
insert heading [one] & Large heading \\
insert heading two & Smaller heading \\
insert heading three & Smaller heading \\
insert heading four & Smaller heading \\
insert heading five & Smaller heading \\
\end{tabularx}

\section{Miscellaneous}
\begin{tabularx}{\linewidth}{ l X}
fraction & Creates a fraction. anything highlighted will form the numerator. \\
over & Creates a fraction with the previous element as the numerator (e.g. "five over three") \\
(super script | to the power) & Superscript \\
sub script & Subscript \\
squared & Superscript 2 \\
cubed & Superscript 3 \\
inverse & Superscript -1 \\
(parens | parentheses) & Parentheses \\
square brackets & Square brackets \\
curly brackets & Curly brackets \\
absolute & Create two bars and moves inside them \\
degrees & Insert a degree symbol \\
summation & $\sum$ \\
% blank summation & $\sum$ \\
% (summation | sum) to N & $\sum^{n}_{?}$ \\
product & $\prod$ \\
% blank product & $\prod$ \\
% product to N & $\sum^{n}_{?}$ \\
limit & $\lim$ \\
% blank limit & $\lim$ \\
label above & Add a label above the selected text \\
label below & Add a label below the selected text \\
\end{tabularx}


\section{Letters}
\subsection{Greek}
By default, all of these commands must be prefixed with "greek" for lowercase or "greek big" for uppercase. This behaviour can be changed by modifying greek\_prefix and capitals\_prefix. Where relevant I have provided pronunciation tips for best results.

\


\begin{longtable}{llll}
alpha & $\alpha$ & & \\
beta & $\beta$ &  & beater \\
gamma & $\gamma$ & $\Gamma$ & \\
delta & $\delta$ & $\Delta$ & \\
epsilon & $\varepsilon$ & & \\
zeta & $\zeta$ & & \\
eta & $\eta$ & & eater \\
theta & $\theta$ & $\Theta$ & they-tah \\
iota & $\iota$ & & \\
kappa & $\kappa$ & & \\
lambda & $\lambda$ & $\Lambda$ & \\
mu & $\mu$ & & moo \\
nu & $\nu$ & & new \\
xi & $\xi$ & $\Xi$ & zee \\
pi & $\pi$ & $\Pi$ & \\
rho & $\rho$ & & \\
sigma & $\sigma$ & $\Sigma$ & \\
tau & $\tau$ & & \\
upsilon & $\upsilon$ & $\Upsilon$ & \\
phi & $\phi$ & $\Phi$ & \\
chi & $\chi$ & & kie \\
psi & $\psi$ & $\Psi$ & sigh \\
omega & $\omega$ & $\Omega$ & \\
\end{longtable}


\subsection{Accents}
These commands add accents above the highlighted text, or create an empty accent if nothing is highlighted.

\

\begin{longtable}{ l l}
accent hat & $\hat{a}$ \\
accent tilde & $\tilde{a}$ \\
accent dot & $\dot{a}$ \\
accent double dot & $\ddot{a}$ \\
accent bar & $\bar{a}$ \\
accent arrow & $\vec{a}$ \\
\end{longtable}


\section{Symbols}

\begin{longtable}{ l l}
[square] root & $\sqrt[n]{x}$ \\
integral & $\int$ \\
double integral & $\int \int$ \\
triple integral & $\int \int \int$ \\
times & $\times$ \\
divide & $\div$ \\
C dot & $\cdot$ \\
plus or minus & $\pm$ \\
partial & $\partial$ \\
infinity & $\infty$ \\
dot dot dot & $\dots$ \\
nabla & $\nabla$ \\
%relations
greater [than] [or] equal [to] & $\geq$ \\
less [than] [or] equal [to] & $\leq$ \\
not equal [to] & $\neq$ \\
approximately [equal] [to] & $\approx$ \\
proportional [to] & $\propto$ \\
preference less [than] & $\prec$ \\
preference less equal & $\preceq$ \\
preference greater [than] & $\succ$ \\
preference greater equal & $\succeq$ \\
% trig
sine & $\sin$ \\
cosine & $\cos$ \\
tangent & $\tan$ \\
secant & $\sec$ \\
cosecant & $\csc$ \\
cotangent & $\cot$ \\
arc sine & $\arcsin$ \\
arc cosine & $\arccos$ \\
arc tan & $\arctan$ \\
hyperbolic sine & $\sinh$ \\
hyperbolic cosine & $\cosh$ \\
hyperbolic tangent & $\tanh$ \\
hyperbolic cotangent & $\coth$ \\
% text
degree & $\deg$ \\
determinant & $\det$ \\
dimension & $\dim$ \\
exponential & $\exp$ \\
(natural (log | logarithm) | log natural) & $\ln$ \\
logarithm & $\log$ \\
argument & $\arg$ \\
maximum & $\max$ \\
minimum & $\min$ \\
(modulo | modulus) & $\bmod$ \\
supremum & $\sup$ \\
infimum & $\inf$ \\
probability & $\Pr$ \\
there exists & $\exists$ \\
member [of] & $\in$ \\
% real numbers & $\mathbb{R}$ \\
% complex numbers & $\mathbb{C}$ \\
% integer numbers & $\mathbb{Z}$ \\
% rational numbers & $\mathbb{Q}$ \\
% natural numbers & $\mathbb{N}$ \\
for all & $\forall$ \\
subset & $\subset$ \\
superset & $\supset$ \\
strict subset & $\subsetneq$ \\
strict superset & $\supsetneq$ \\
intersection & $\cap$ \\
union & $\cup$ \\
logic and & $\land$ \\
logic or & $\lor$ \\
logic not & $\lnot$ \\
left arrow & $\leftarrow$ \\
right arrow & $\rightarrow$ \\
up arrow & $\uparrow$ \\
down arrow & $\downarrow$ \\
left right arrow & $\leftrightarrow$ \\
maps to & $\mapsto$ \\
oh plus & $\oplus$ \\
oh times & $\otimes$ \\
big oh plus & $\bigoplus$ \\
big oh times & $\bigotimes$ \\
diagonal dots & $\ddots$ \\
horizontal dots & $\cdots$ \\
vertical dots & $\vdots$ \\
\end{longtable}


\section{Fractions}
There are a few ways of easily inserting fractions:

\begin{itemize}
\item Use the "fraction" command, and navigate through it using directions.
\item Use the "over" command, which will build a fraction with the previous element as the numerator. e.g. "x-ray squared over five".
\item For denominators up to 10, use their natural names, providing a number for the numerator, e.g. "five thirds".
\end{itemize}

\section{Nested commands}
There are a few commands within Mathfly which allow for commands to be inserted within them. These are just examples, you can include any commands you want:
\begin{itemize}
\item ``Integral from minus infinity to infinity'' - integral symbol with superscript and subscript.
\item ``Definite from zero to ten'' - definite integral square brackets with subscript and superscript afterwards.
\item ``Differential x-ray squared by squared yankee'' - creates a differential friction.
\item ``Sum from india equals one to november'' - creates a summation.
\item ``Limit from november to infinity'' - create a limit.
\item ``argument that maximises greek beta'' - argmax.
\item ``minimum by greek beta'' - min.
\item ``sub india'' - quick sub/superscripts.
\end{itemize}


\section{Matrices}
\begin{itemize}
\item To insert a matrix of a particular size, use the matrix command, e.g. "matrix three by one".
\item To add or remove columns and rows, Use the command "add/remove matrix column/row".
\item Matrices can be encased in brackets as expected, E.g. "parens matrix three by three".
\end{itemize}

\section{Units}
These commands insert common scientific units. By default, all of them must be prefixed with "unit", so for example "unit cubic feet" produces ft$^{3}$.
\begin{itemize}
\item \textbf{Activity}--- ~
Becquerels,
Curies

\item \textbf{Amount}--- ~
Attomoles,
Examoles,
Femtomoles,
Gigamoles,
Kilomoles,
Megamoles,
Micromoles,
Millimoles,
Moles,
Nanomoles,
Petamoles,
Picomoles,
Teramoles

\item \textbf{Area}--- ~
Acres,
Hectares,
Square feet,
Square inches,
Square metres

\item \textbf{Current}--- ~
Amperes,
Kiloamperes,
Microamperes,
Milliamperes,
Nanoamperes

\item \textbf{Capacitance}--- ~
Farads,
Microfarads,
Millifarads,
Nanofarads,
Picofarads

\item \textbf{Charge}--- ~
Coulombs

\item \textbf{Conductance}--- ~
Kilosiemens,
Microsiemens,
Millisiemens,
Siemens

\item \textbf{Potential difference}--- ~
Kilovolts,
Megavolts,
Microvolts,
Millivolts,
Nanovolts,
Picovolts,
Volts

\item \textbf{Resistance}--- ~
Gigaohms,
Kiloohms,
Megaohms,
Milliohms,
Ohms

\item \textbf{Energy}--- ~
British thermal unit,
Calories,
Electron volts,
Ergs,
Gigaelectronvolts,
Gigajoules,
Joules,
Kilocalories,
Kilojoules,
Megaelectronvolts,
Megajoules,
Microjoules,
Millijoules,
Nanojoules

\item \textbf{Force}--- ~
Dynes,
Kilonewtons,
Meganewtons,
Micronewtons,
Millinewtons,
Newtons,
Ounce force,
Pound force

\item \textbf{Frequency}--- ~
Exahertz,
Gigahertz,
Hertz,
Kilohertz,
Megahertz,
Petahertz,
Terahertz

\item \textbf{Illuminance}--- ~
Footcandle,
Lux,
Phot

\item \textbf{Length}--- ~
Angstrom,
Attometers,
Centimeters,
Decimeters,
Femtometers,
Feet,
Inches,
Kilometers,
Meters,
Micrometers,
Miles,
Millimeters,
Nanometers,
Picometers

\item \textbf{Luminance}--- ~
Candela,
Lumens

\item \textbf{Magnetic flux}--- ~
Maxwells,
Microwebers,
Milliwebers,
Nanowebers,
Webers

\item \textbf{Magnetic flux density}--- ~
Gauss,
Microteslas,
Milliteslas,
Nanoteslas,
Picoteslas,
Teslas,
Henries,
microhenries,
millihenries

\item \textbf{Mass}--- ~
Atomic mass units,
Centigrams,
Decigrams,
Grams,
Kilograms,
Micrograms,
Milligrams,
Pounds,
Slug

\item \textbf{Angle}--- ~
degrees,
Microradians,
Milliradians,
Minutes of angle,
Seconds of angle,
Radians,
Steradian

\item \textbf{Power}--- ~
Gigawatts,
Horsepowers,
Kilowatts,
Megawatts,
Microwatts,
Milliwatts,
Nanowatts,
Watts

\item \textbf{Pressure}--- ~
Atmospheres,
Bar,
Kilobar,
Kilopascals,
Megapascals,
Micropascals,
Millibar,
Millimeters of Mercury,
Pascals,
Torrs

\item \textbf{Temperature}--- ~
Celsiuss,
Fahrenheits,
Kelvins

\item \textbf{Time}--- ~
Attoseconds,
Days,
Femtoseconds,
Hours,
Microseconds,
Milliseconds,
Minutes,
Nanoseconds,
Picoseconds,
Seconds,
Years

\item \textbf{Volume}--- ~
Cubic feet,
Cubic inches,
Cubic metres,
Gallons,
Liters,
Milliliters,
Pints,
Quarts
\end{itemize}
\end{document}